Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics

### 2018-12-12 scagnostics.Rmd
Updated spiral guided tour example.

distanceToSp <- function(planes, specialPlane){
  planes <- as.list(planes)
  maxI <- length(planes)
  distL <- numeric(maxI)
  i <- 1
  while(i<maxI+1){
    cDist <- proj_dist(planes[[i]], specialPlane)
    distL[i] <- cDist
    i <- i+1
  }
  return(distL)
  }
if(!file.exists("cache/findspiral.rda")){
  distDf <- tibble(d=numeric(), distance=numeric())
  distToSp <- tibble(d=numeric(), distance=numeric(), t=numeric())

  maxBases <- 100
  fViewL <- list()
  allPlanes <- list()
  i <- 1
  for(d in c(4,6,8)){
    set.seed(1779+d)
    specialPlane <- matrix(c(rep(0,d-2),1,0,rep(0,d-1),1),ncol=2)
    spiralD <- spiralData(d, 1000) %>% scale() %>% as_tibble()
    spiralTour <- save_history(spiralD, guided_tour(scagIndex("Skinny"), search_f = tourr:::search_better,
                                                    max.tries = 5000, cooling = 1, alpha = pi),
                              max_bases = maxBases)
    if(d==4){maxBases <- min(maxBases, length(spiralTour))}
    distDf <- rbind(distDf, tibble(d=d, distance=distanceDist(spiralTour)))
    distToSp <- rbind(distToSp, tibble(d=d, distance=distanceToSp(spiralTour, specialPlane), t=1:maxBases))
    fView <- as.tibble(as.matrix(spiralD) %*% as.list(spiralTour)[[maxBases]])
    fViewL[[i]] <- ggplot(fView, aes(V1, V2)) + geom_point()
    allPlanes[[i]] <- spiralTour
    i <- i+1
  }
  save(distDf, distToSp, fViewL, allPlanes, file = "cache/findspiral.rda")
} else {
  load("cache/findspiral.rda")
}

p1 <- ggplot(distDf, aes(group=d, y=distance, x=d)) + geom_boxplot()
p2 <- ggplot(distToSp, aes(color=as.factor(d),x =t, y=distance)) +
  geom_point() +
  labs(y = "Distance to special view", color = "d")

>>>>

distanceToSp <- function(planes, specialPlane){
  planes <- as.list(planes)
  maxI <- length(planes)
  distL <- numeric(maxI)
  i <- 1
  while(i<maxI+1){
    cDist <- proj_dist(planes[[i]], specialPlane)
    distL[i] <- cDist
    i <- i+1
  }
  return(distL)
  }

if(!file.exists("cache/findspiral.rda")){
  distDf <- tibble(d=numeric(), distance=numeric())
  distToSp <- tibble(d=numeric(), distance=numeric(), t=numeric())

  maxBases <- 100
  fViewL <- list()
  allPlanes <- list()
  i <- 1
  for(d in c(4,5,6)){
    set.seed(58958)
    specialPlane <- matrix(c(rep(0,d-2),1,0,rep(0,d-1),1),ncol=2)
    spiralD <- spiral1000 %>%
      purrr::when(d<6 ~ select(., -V4), ~ .) %>%
      purrr::when(d<5 ~ select(., -V3), ~ .)
    spiralTour <- save_history(as.matrix(spiralD),
                               guided_tour(scagIndex("Skinny"), search_f = tourr:::search_better,
                                                    max.tries = 5000, cooling = 1, alpha = pi),
                              max_bases = maxBases)
    #if(d==4){maxBases <- min(maxBases, length(spiralTour))}
    nBases <- length(spiralTour)
    distDf <- rbind(distDf, tibble(d=d, distance=distanceDist(spiralTour)))
    distToSp <- rbind(distToSp, tibble(d=d, distance=distanceToSp(spiralTour, specialPlane), t=1:nBases))
    fView <- as.tibble(as.matrix(spiralD) %*% as.list(spiralTour)[[nBases]])
    fViewL[[i]] <- ggplot(fView, aes(V1, V2)) + geom_point()
    allPlanes[[i]] <- spiralTour
    i <- i+1
  }
  save(distDf, distToSp, fViewL, allPlanes, file = "cache/findspiral.rda")
} else {
  load("cache/findspiral.rda")
}

p1 <- ggplot(distDf, aes(group=d, y=distance, x=d)) +
  geom_boxplot() +
  scale_x_continuous(breaks = c(4, 5, 6))
p2 <- ggplot(distToSp, aes(color=as.factor(d),x =t, y=distance)) +
  geom_point() +
  labs(y = "Distance to special view", color = "d")
